Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
deleted a paragraph from the results section

The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$. Considering a one-dimensional field, the connectivity kernel is decomposed using,

@@

\section{Results}
To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 200 realizations of 1 second of data were generated. The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$). The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The firing rate slop, $\varsigma$ was set to $0.56  ~mV^{-1}$. The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations. The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.  \ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table} The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states. \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}  
% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}

>>>>

The multi-resolution approximation of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(.)$, and the connectivity kernel, $w(.)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$. Considering a one-dimensional field, the connectivity kernel is decomposed as,

@@

\section{Results}
To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using \eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, enabling a comparison between true and estimated parameters. 200 realizations of 1 second of data were generated. The observation noise was set to $\boldsymbol\Sigma_{\epsilon}=0.1 \times \mathbf{I}_{n_y}$ and the disturbance covariance was set to $\eta(r-r') = \phi_{3,-2}(r-r')$ (B-spline, $j=3$). The sampling period and the synaptic time constant were set to $T_s = 1$~ms and $\tau = 10$~ms, respectively. The firing rate slop, $\varsigma$ was set to $0.56  ~mV^{-1}$. The distance between adjacent sensors was $0.5$~mm resulting into $n_y = 161$ observations. The observation kernel was modeled using a B-spline function, with a width of 0.8~mm at half the maximum amplitude. The spacing and bandwidth of the sensors allowed for the full spatial bandwidth of the field to be observed.  \ken{if we need to gain space I would remove the rest of this paragraph and put all parameters in a table} The spatial cutoff frequency of the observed field, $y_t(r_n)$, was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of \dean{6?}, the cutoff spatial frequency was \dean{$\nu_{cy} = ??$} cycles/mm \cite{Freestone2011}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states.

% \dean{With this number of observations, the estimation problem was well-posed, since the wavelets are orthogonal and the number of states, $n_x < n_y$ at each level of the decomposition.}  
% \cut{Note that wavelets due to their bandpass filter characteristics extract successively higher and higher frequency components by increasing $j$.}
